---
title: "Novel Coronavirus is intractable, should reduce close cutests to prevent outbreaks"
author: "Xuanmo Wang"
date: 2020-09-27T21:13:14-05:00
categories: ["R"]
tags: ["R Markdown", "plot", "regression"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```

# Abstract

The virus of COVID19 speared in a high spearing rate recently, the data from the opendatatoronto data  base is to illustrate the distribution of the virus spearing in Toronto among the age groups and ways of getting infected.

# Variables of Data

Source of Infection 
The most likely way that sporadic cases acquired their COVID-19 infection. Only the most likely exposure for each case is reported. Exposures that occurred up to 14 days before symptoms start are potential acquisition sources, and can include: Travel:Travel outside of Ontario.
Close contact with a case: Was in close contact with a confirmed or probable COVID-19 case (e.g., reside in the same household).
Institutional setting: Institutional settings includes, but not limited to: long-term care homes, acute care hospitals, complex case hospitals, special care facilities, retirement homes, rehabilitation hospitals.
Healthcare setting: Healthcare settings includes, but not limited to: family physician, dentist, ophthalmologist, sports doctor.
Community: Cases with no reported travel outside of Ontario, no known close contact with a COVID-19 case, and no reported infection acquired in an institutional or healthcare setting.
Pending Information on source of infection pending.
Unknown/missing Source of infection not identified or missing.
N/A: Outbreak-associated cases.

# Young people between the ages of 20 and 29 have the highest number of infections
About the COVID19, there are big amount of people were getting infected by the virus. The age groups were from 19 years old to 90 years old. Here is a set of data by using histogram to provide the distribution of the age group
```{r}
####Instal Data

library(opendatatoronto)
library(dplyr)

# get package
package <- show_package("64b54586-6180-4485-83eb-81e8fae3b8fe")
package

# get all resources for this package
resources <- list_package_resources("64b54586-6180-4485-83eb-81e8fae3b8fe")

# identify datastore resources; by default, Toronto Open Data sets datastore resource format to CSV for non-geospatial and GeoJSON for geospatial resources
datastore_resources <- filter(resources, tolower(format) %in% c('csv', 'geojson'))

# load the first datastore resource as a sample
DATA <- filter(datastore_resources, row_number()==1) %>% get_resource()
DATA
glimpse(DATA)
library(tidyverse)

Episode.Date=DATA$`Episode Date`
Age.Group=DATA$`Age Group`
Source.of.Infection=DATA$`Source of Infection`

ggplot(data=DATA, aes(x = Age.Group)) + geom_histogram(color=5, fill='blue', bins = 10, stat = 'count')
```
As the distribution provided here, the graph follows a right-skewed distribution and it does not looks like a symmetric distribution. The bins shows that most of the people who get infected is the age group around 20 and 29 years old. These people got highest number of infecting by the virus.



# The Ways Of Getting Infected
There are many ways of getting infection by the virus, such as getting close contact, or spears by the community, healthcare issues, institutional facts … etc. Let’s illustrate the reasons and find some trend of getting infection.
```{r}
ggplot(data=DATA, aes(x = Source.of.Infection)) + geom_histogram(color=83, fill='green', bins = 10, stat = 'count')
```
As the graph shows, the thing that we can see clearly is the the close contact and the outbreak associated becomes plays the majority of ways of getting infected. The two ways have around 6000 of people separately. There are also many people get infected by the other reason of community as around 2500 people. The graph is not symmetric either does not like to be following a normal distribution.


# Conclusion

In conclusion, the people in the age group around 19 to 29 should be aware of the COVID19 because it is the group that many of them getting infected. The majority way of getting infected is by outbreak and Close contact with a case.

#Reference

Opendata:https://open.toronto.ca/dataset/covid-19-cases-in-toronto/
